\Title

### 2020-12-09 manuscript/manuscript.tex
Minor change to trigger a build
Add data weights to the equations

% Define inverse symbol with shorter minus
\newcommand{\inv}{^{\text{-}1}}

@@

\begin{equation}
    \phi(\mathbf{c}) =
        \left\lVert
            \mathbf{d}^o - \mathbf{A}\mathbf{c}
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c} \right\rVert ^2,
    \label{eq:misfit-unscaled}
\end{equation}

\noindent where $\left\lVert \cdot \right\rVert$ symbolizes the L$_2$ norm and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.

@@

The misfit function defined on equation~\ref{eq:misfit-unscaled} can be
rewritten as

\begin{equation}
    \phi(\mathbf{m}) =
        \left\lVert \mathbf{d}^o
        - \mathbf{B}\mathbf{m} \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{m} \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

@@

\begin{equation}
    \hat{\mathbf{m}} =
        \left[
            \mathbf{B}^\text{T} \mathbf{B}
            + \lambda \mathbf{I}
        \right]\inv
        \mathbf{B}^\text{T}
        \mathbf{d}^o.
\end{equation}

On the other hand, if there are more sources than observation points, the
problem is under-determined and the scaled coefficients can be obtained as
\citep{menke1989}:

\begin{equation}
    \hat{\mathbf{m}} =
    \mathbf{B}^\text{T}
        \left[
            \mathbf{B} \mathbf{B}^\text{T}
            + \lambda \mathbf{I}
        \right]\inv
        \mathbf{d}^o.
\end{equation}

@@

Lets assume we have $N$ measurements of a harmonic field on observations points
$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
different sets of equivalent sources: we define $K$ overlapping windows of
equal size that cover the whole observation area, and then we create one set of
equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
sources that fall inside the $k$-th window.
The observed data should be equal to the superposition of the
effect of every set of equivalent sources:

@@

\begin{equation}
    \alpha_k = \frac{
        \mathbf{r}_{k-1}^T \mathbf{A}_k \mathbf{c}_k
    }{
        \left(\mathbf{A}_k \mathbf{c}_k\right)^T \mathbf{A}_k \mathbf{c}_k
    }.
\end{equation}

>>>>

% Define inverse symbol with shorter minus
\newcommand{\inv}{^{\text{-}1}}
\newcommand{\trans}{^{\text{T}}}

@@

\begin{equation}
    \phi(\mathbf{c}) =
    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]\trans
    \mathbf{W}
    \left[\mathbf{d}^o - \mathbf{A}\mathbf{c}\right]
    + \lambda_d\ \mathbf{c}\trans\mathbf{c}
    \ ,
    \label{eq:misfit-unscaled}
\end{equation}

\noindent where
$\mathbf{W}$ is a $N \times N$ matrix of data weights and
$\lambda_d$ is a positive \emph{damping} parameter with the same units as the
Jacobian matrix elements.
The second term on the right-hand side of the equation is a zeroth-order
Tikhonov regularization \citep{tikhonov1977} (also known as a damping
regularization or ridge regression) that is used to stabilize the solution.

@@

The goal function defined on equation~\ref{eq:misfit-unscaled} can be
rewritten as

\begin{equation}
    \phi(\mathbf{m}) =
    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]\trans
    \mathbf{W}
    \left[\mathbf{d}^o - \mathbf{B}\mathbf{m}\right]
    + \lambda\ \mathbf{m}\trans\mathbf{m}
    \ ,
    \label{eq:misfit}
\end{equation}

@@

\begin{equation}
    \hat{\mathbf{m}} =
    \left[
      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
    \right]\inv
    \mathbf{B}\trans\mathbf{W}
    \mathbf{d}^o.
\end{equation}

@@

Lets assume we have $N$ measurements of a harmonic field on observations points
$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
\ldots, d_N)\trans$. We have defined a set of $M$ point sources located on
$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
different sets of equivalent sources: we define $K$ overlapping windows of
equal size that cover the whole observation area, and then we create one set of
equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
sources that fall inside the $k$-th window.
The observed data should be equal to the superposition of the
effect of every set of equivalent sources:

@@

\begin{equation}
    \alpha_k = \frac{
        \mathbf{r}_{k-1}\trans \mathbf{A}_k \mathbf{c}_k
    }{
        \left(\mathbf{A}_k \mathbf{c}_k\right)\trans \mathbf{A}_k \mathbf{c}_k
    }.
\end{equation}
